Higher-Order unification for free!

### 2024-04-12 paper/main.tex
sec 10

In this paper we show how to lift the meta language higher-order
unification procedure to the object language. The resulting
unification honours $\eta\beta$-equivalence for

>>>>

In this paper we show how to lift the meta language higher-order unification
procedure to the object language. Our proposed approach is highly adaptable to
align closely with the behavior of the object language. It is not tightly
coupled with the Coq system but can serve as a flexible framework for meta
programming in any ML.

Our encoding leverages the advantage of not needing to recode the unification
algorithm of the object language. Instead, it utilizes the unification of the
meta language facilitated by the various links we establish to handle
``problematic'' subterms. Additionally, our encoding benefits from the
application of indexing algorithms for static clause filtering.

Furthermore, the unification process we propose is tailored for potential future
implementations of tabled search, incorporating memoization to retrieve
solutions from previous searches.

---
